Storm surges in the Strait of Georgia simulated with a regional model

### 2015-06-09 AO_guides/manuscriptAO.tex
Added tide-killing

Sea surface height anomaly (or remote forcing) was set uniformly across the mouth of Juan de Fuca using values from the Tofino tide gauge \citep{DFOObservations} which is outside of, but close to, the western boundary of the model domain (Figure \ref{fig:domain}).  A monthly climatology was produced using daily averages from 2000-2010, binning them by month, averaging and setting the yearly mean to zero.  For the storm surge simulations, hourly variations in sea surface height were used.  These values are the Tofino tide gauge values with the tides removed. {\color{red}Tidal predictions were generated with the tidal analysis package called t\_tide \citep{pawlowicz2002classical} using a time series from the year of the storm surge. A harmonic analysis was performed for 67 constituents. In order to prevent over-predicted constituents due to high surge years, the time series was first filtered by applying a Doodson filter \citep{parker2007NOAA} and periods with large non-tidal amplitudes were removed. Long period constituents such as Sa, Ssa, etc were not used in the tidal predictions since these constituents are often contaminated by non-tidal energy from seasonal meteorological trends. Further, constituents with a low signal to noise ratio were neglected. } The storm surge simulations also used the sea surface height anomaly from Port Hardy, forced at the northern boundary in Johnstone Strait.

>>>>

Sea surface height anomaly (or remote forcing) was set uniformly across the mouth of Juan de Fuca using values from the Tofino tide gauge \citep{DFOObservations} which is outside of, but close to, the western boundary of the model domain (Figure \ref{fig:domain}).  A monthly climatology was produced using daily averages from 2000-2010, binning them by month, averaging and setting the yearly mean to zero.  For the storm surge simulations, hourly variations in sea surface height were used.  These values are the Tofino tide gauge values with the tides removed. {\color{red}Tidal predictions were generated with the tidal analysis package called t\_tide \citep{pawlowicz2002classical} using a time series from the year of the storm surge. A harmonic analysis was performed for 67 constituents. In order to prevent over-predicted constituents due to high surge years, the time series was first filtered by applying a tide-killing Doodson filter \citep{parker2007NOAA} and periods with large non-tidal amplitudes were removed. Long period constituents such as Sa, Ssa, etc were not used in the tidal predictions since these constituents are often contaminated by non-tidal energy from seasonal meteorological trends. Further, constituents with a low signal to noise ratio were neglected. } The storm surge simulations also used the sea surface height anomaly from Port Hardy, forced at the northern boundary in Johnstone Strait.
